Meta-analysis fungicide efficacy FHB

### 2017-07-10 fhb-meta.Rmd
Updated spreadsheet
Change

---
title: "Netwwork meta-analysis of the effect of fungicides for FHB control in Brazil"
output: github_document
---

>>>>

---
title: "Meta-analysis fungicide efficacy FHB"
author: "Franklin Machado & Emerson Del Ponte"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: leonids
    highlight: vignette
---
